On a Alfvenicity of solar wind discontinuities

### 2024-10-04 article.qmd
update

In this model, we assume that the asymptotic boundary conditions are known from measurements, including the normal component of the magnetic field and the asymptotic properties of the incident fluid streams, which are clearly distinguishable. It should be noted, however, that while the velocity space boundary between different groups may be clear in the uniform field region outside the current sheet, within the sheet itself, the boundary can become more complex. For instance, individual ions may jump from one group to another, and some may become trapped within the current sheet. These complexities, particularly ion behavior within the sheet, are beyond the scope of this paper and are not addressed in the current analysis.

@@

The multifluid model developed above is used here to study a specific example and the effects of model parameters: assume a density profile for one species taking the form of a Gaussian function

>>>>

In this model, we assume that the asymptotic boundary conditions are known from measurements, including the normal component of the magnetic field, the magnitude of the magnetic field, and the asymptotic properties of the incident fluid streams. It should be noted, however, that while the velocity space boundary between different groups may be clear in the uniform field region outside the current sheet, within the sheet itself, the boundary can become more complex. For instance, individual ions may jump from one group to another, and some may become trapped within the current sheet. These complexities, particularly ion behavior within the sheet, are beyond the scope of this paper and are not addressed in the current analysis.

@@

The multifluid model developed above is used here to study a specific example and the effects of model parameters: assume a density profile for one species taking the form of a Lorentzian function with a background density.
